\chapter*{Acknowledgments}
I would, first of all, extend my gratitude to Dr. Norato and Dr. Toropov for accepting to review this thesis and Dr. Allaire and Dr. Bartoli for agreeing to be part of the jury. 
 This research work being a CIFRE thesis gave me the opportunity to work both in an academic environment (ISAE and ICA Toulouse) and in a company (Airbus Operations S.A.S.). On the academic side, I would like to thank both my advisors Dr. Christian Gogu and Dr. Joseph Morlier. They trusted my research and my ideas and provided very useful feedbacks. They made me feel capable of doing great things. Their advice now is part of my attitude at work. Double checking is also part of my life now.\\
 At Airbus, I thank my advisor Rémi Amargier, who leaded my research activity and discussed with me way forward to maximize the impact of my developments among my colleges.\\
 
 I thank ESYT team at Airbus, my coworkers on the plateau and the researcher in ICA lab for trusting the value of my contribution and for fruitful discussions that helped developing my research. I thank all the ISAE master students and all interns I had the chance to mentor in the last 3 years. They also helped me with my personal and professional development.\\
 
 I want to extend my thanks to my wife who supported my passion for my research and helped me achieving all my personal and professional goals. I thank also my family for investing in my success and believing in me.\\
 
 I want also to extend my gratitude to all researchers I have discussed with in conferences that also gave me valid hints for improving my framework among others Dr. Xu Guo, Dr. Weisheng Zhang, Dr. Oded Amir, Dr. Niels Aage, again Dr. Julian Norato, Dr. H Alicia Kim, Dr. Frédéric Duboeuf and Dr. Anders Klarbring. 
 

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../phdthesis"
%%% End:
